Article title

### 2018-10-02 docs/rupee.tex
remove table

Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features amenable to big data processing.
Protein structure searches that use linear encodings are not unique \cite{Carpentier2005,Daniluk2011,Ritchie2012}.
The novelty of our approach lies in its remarkable performance given its simplicity. 
Additionally, elements of our approach can be isolated and found to be useful in their own right.

@@

\tablename~\ref{tab:codes} summarizes the mapping between region and secondary structure assignment combinations and ranges of integer valued descriptors.  
The specific mapping was arrived at primarily based on an evaluation of results.

@@

\begin{table}[t]
    \caption{DSSP Code/Descriptor Map}
    \label{tab:codes}
\centering
\begin{tabular}{lll}
\toprule
    \head{DSSP Codes} & \head{SS} & \head{Descriptors}\\
\midrule
    G, H, I & helix & 1-4\\
    E & strand & 5-7\\
    S, C & bend, coil & 8-10\\
    T & turn & 11\\
    B & bridge & 12\\
\bottomrule
\end{tabular}
\end{table}

>>>>

Broadly, we define a linear encoding of protein structure and convert this linear encoding into a bag of features. 
Min-hashing and locality sensitive hashing (LSH), techniques drawn from big-data, are then applied to implement a protein structure indexing method that serves as the foundation for both RUPEE operating modes, fast and slow.

Protein structure searches that use linear encodings are not unique \cite{Carpentier2005,Daniluk2011,Ritchie2012}.
The novelty of our approach lies in its remarkable performance given its simplicity. 
Additionally, elements of our approach can be isolated and found to be useful in their own right.

@@

@@
